### 2018-07-03 pilot_manuscript.Rmd
made a few small edits
Mostly want to ask you about the MLMs we did and figure out the best approach for the results section.

## Procedure

@@

@@

@@

@@

>>>>

## Procedure
Using the *rvest* library in the statistical package *R*, we pulled body text for individual articles from each of the aforementioned sources (identified using CSS language) and compiled them into a dataset [@CITE_rvest]. Using this dataset, we identified word count and average word count per source. This process was run once daily starting on *DATE* until *DATE.* Starting on *DATE,* the process was run twice daily - once in the morning and again in the evening. Data collection was terminated once 250,000 words per source was collected on *DATE.*

@@

Once data collection ended, the text was scanned using the *ngram* package in *R* [@CITE_ngram]. This package includes a word count function, which was used to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites. At this point, duplicate articles were discarded.

@@

In order to fully capture the evaluative power of the Moral Foundations Dictionary (MFD; *CITE*), forms and conjugations of words were added to the original MFD. For example, *abuse* was supplemented with *abusive*, *abuser*, *abused*, and *abusing*. Once additional word forms were added, the words making up each of the five foundations in the MFD were split among positive and negative dimensions (i.e., *abide* as a postive authority/respect word and *defect* as a negative authority/respect word).

@@

Once the MFD was separated along lines of positive and negative, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm]. The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*). The same procedure was applied to the MFD words, and the addition of multiple forms of each concept allowed for the capture of all versions of stemming that might occur given *tm*'s English stemmer function. The article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a sum and percentage of their occurence.

@@

Using the *nlme* library in *R*, a 2 (Political Lean) by 5 (MFD area) multillevel model with news source as a random intercept was analyzed to control for correlated error between articles published in the same news source. An intercept-only model was compared to a random intercept model with the news sources as the random factor, and ...SAY HERE WHAT HAPPENED? PROB A TABLE OF THE MODEL #S.

#stopped here to ask questions

Next, a predictor model with political lean predicting percent of MFD words, a model adding MFD category (i.e. "harm-positive," "harm-negative", etc.) as a predictor, and a model with the interaction of political lean and MFD category predicting percent were run. Finally, a series of 10 models were run with political lean predicting percent split into the 10 MFD categories.
